Capon Beamforming Applied on Moving Objects - An Analysis of Local Shift-Invariance

### 2013-10-31 HRUIofMovingObjects/jrnl_article.tex
Moving targets paper: done some writing

In order to visualize the local lateral shift-invariance of a given imaging system, we will use lateral shift-variance plots (LSV-plots), introduced by Hergum \textit{et al.} \cite{Hergum2007}. A LSV-plot is constructed for a given imaging system by imaging a laterally moving point scatterer. For each lateral position the root-mean-square (RMS) is calculated in range, and the resulting beam profiles are stacked in order to produce an image. The image is in this paper displayed as a contour plot with contours on -1, -2, -3, -6, -12 and -24 dB. The maximum for each beam profile is also marked with a black dot. The system is said to be local lateral shift-invariant if the contours are diagonal, hence the diagonals have constant amplitude.

To further quantify the shift-invariance we have calculated the mean absolute error (MAE) of the maximum point in each beam profile versus $f(x)=x$, and the MAE of the amplitude variation for the same set of points. The first number quantifies the amount of geometric distortion, and the latter quantifies the gain variation or in our case the loss of signal. The maximum amplitude deviation along the max-point trace is also measured. We present all these numbers together with the LSV-plots.

Fig.\,\ref{fig:das_shiftinvariant} presents a LSV-plot for an imaging system using DAS beamforming with a beam spacing equal to (\ref{eq:resolution}). The red dotted vertical lines indicates the position of tx-rx beams. The point scatterer response has been simulated using Field II \comment{add citations}. We see that the contours are approximately diagonal and therefore we can conclude that the system is lateral shift-invariant. The P-MAE and A-MAE are also minimal. \comment{Why is the scallop loss only 0.78 dB when Fig. 1 says it could be 3.92?}. In Fig.\,\ref{fig:das_shiftvariant} the beam spacing is reduced by a factor of two. We see that the scallop loss increases to a level where the contours no longer are diagonal. This loss can not be reconstructed through IQ or in-coherent interpolation, the max peak is forever lost when the point is located between two beams and the distance between the two beams are to high.

\begin{figure*}[!t]
\centerline{
\subfloat[]{\includegraphics[width=0.5\linewidth]{\img das_normal2.eps}\label{fig:das_shiftinvariant}}
\hfill{}
\subfloat[]{\includegraphics[width=0.5\linewidth]{\img das_undersampled2_2x.eps}\label{fig:das_shiftvariant}}
}
\caption{...}
\label{fig:das}
\end{figure*}

\section{Local Lateral Shift-Invariance of the Capon Beamformer}
We will now investigate the lateral local shift-invariance of the Capon beamformer with parameters equal to the once used in earlier work \comment{cite}. A  . Fig.\,\ref{fig:capon1}.

@@

\section{Oversampling on Transmit}
The typical way of obtain sufficient sampling in active broadband application is by  increasing the number of transmit beams until (\ref{eq:resolution}) is fulfilled.  If the number of tr

\begin{figure*}[!t]
\centerline{
\subfloat[]{
\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=001_2x.eps}
}
\subfloat[]{
\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=001_4x.eps}
}
}
\caption{...}
\label{fig:capon_oversampling}
\end{figure*}

@@

\begin{figure*}[!t]
	\centerline{
		\subfloat[]{
			\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=001_2x_microsteering_correct_pitch.eps}
		}
		\subfloat[]{
			\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=001_4x_microsteering_correct_pitch.eps}
		}
	}
	\caption{...}
	\label{fig:benchmark_capon_bs}
\end{figure*}

@@

@@

@@

>>>>

In order to visualize the local lateral shift-invariance of a given imaging system, we will use lateral shift-variance plots (LSV-plots), introduced by Hergum \textit{et al.} \cite{Hergum2007}. A LSV-plot is constructed for a given imaging system by imaging a laterally moving point scatterer. For each lateral position the root-mean-square (RMS) is calculated in range, and the resulting beam profiles are stacked in order to produce an image. The LSV-plots in this paper are displayed as a contour plot with contours on -1, -2, -3, -6, -12 and -24 dB. In a ultrasound image with 256 gray levels and 50 dB dynamic range 1 dB will corresponds to 5 gray levels. Depending on the surroundings, this is around the lowest difference a human being can detect \comment{need reference}. A loss larger than 1dB will therefore be visible in the image. The maximum for each beam profile is also marked with a black dot. The system is said to be local lateral shift-invariant if the contours are diagonal, hence the diagonals have constant amplitude.

To further quantify the shift-invariance we have calculated the mean absolute error (MAE) of the maximum point in each beam profile versus $f(x)=x$, and the MAE of the amplitude variation for the same set of points. The first number quantifies the amount of geometric distortion, and the latter quantifies the gain variation or in our case the loss of signal. The maximum amplitude deviation along the max-point trace is also calculated and reported. We present all these numbers together with the LSV-plots.

Fig.\,\ref{fig:das_shiftinvariant} presents a LSV-plot for an imaging system using DAS beamforming with a beam spacing equal to (\ref{eq:resolution}). The red dotted vertical lines indicates the position of tx-rx beam pairs. The point scatterer response has been simulated using Field II \comment{add citations} \comment{add table with simulation settings}. We see that the contours are approximately diagonal and therefore we can conclude that the system is locally lateral shift-invariant. The P-MAE and A-MAE are also minimal. \comment{Why is the scallop loss only 0.78 dB when Fig. 1 says it could be 3.92?}. In Fig.\,\ref{fig:das_shiftvariant} the beam spacing is reduced by a factor of two. We see that the scallop loss (max A-MAE) increases to a level where the contours no longer are diagonal. The maximum peak is lost when the point is located between two beams and the distance between the two beams are too high.

\begin{figure*}[!t]
\centerline{
\subfloat[]{\includegraphics[width=0.5\linewidth]{\img das_normal2.eps}\label{fig:das_shiftinvariant}}
\hfill{}
\subfloat[]{\includegraphics[width=0.5\linewidth]{\img das_undersampled2_2x.eps}\label{fig:das_shiftvariant}}
}
\caption{LSV-plots of DAS beamforming. If the contours are diagonal the imaging system is said to be lateral local shif-invariant. Red vertical lines are plotted where tx-rx beams are located. a) Sampling corresponding to (\ref{eq:resolution}). b) Undersampling with a factor two.}
\label{fig:das}
\end{figure*}

\section{Local Lateral Shift-Invariance of the Capon Beamformer}
We will now investigate the local lateral shift-invariance of the Capon beamformer with parameters equal to the once used in earlier work \comment{cite}. A  . Fig.\,\ref{fig:capon1}.

@@

\subsection{Oversampling on Transmit}
The typical way of obtain sufficient sampling in active broadband application is by  increasing the number of transmit beams until (\ref{eq:resolution}) is fulfilled.  If the number of tr

\begin{figure*}[!t]
\centerline{
\subfloat[]{
%\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=001_2x.eps}
}
\subfloat[]{
%\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=001_4x.eps}
}
}
\caption{Oversampling on transmit ...}
\label{fig:capon_oversampling}
\end{figure*}

@@

\begin{figure*}[!t]
	\centerline{
%		\subfloat[]{
%			\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=001_2x_microsteering_correct_pitch.eps}
%		}
%		\subfloat[]{
%			\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=001_4x_microsteering_correct_pitch.eps}
%		}
	}
	\caption{Oversampling using phase rotation ...}
	\label{fig:benchmark_capon_bs}
\end{figure*}

@@

\begin{figure}\caption{Plot of contrast vs oversampling factor (phase rotation) in in-vivo data.}
\end{figure}

@@

\begin{figure*}[!t]
\centerline{
%\subfloat[]{\includegraphics[width=0.3\linewidth]{\img das_normal2.eps}\label{fig:das_shiftinvariant}}
\hfill{}
%\subfloat[]{\includegraphics[width=0.3\linewidth]{\img das_normal2.eps}\label{fig:das_shiftinvariant}}
\hfill{}
%\subfloat[]{\includegraphics[width=0.3\linewidth]{\img das_undersampled2_2x.eps}\label{fig:das_shiftvariant}}
}
\caption{LSV-plots of in-vitro data. a) Image of the data. b) Normal. c) Oversampling with phase rotation}
\label{fig:das}
\end{figure*}

@@

\begin{figure*}[!t]
\centerline{
%\subfloat[]{\includegraphics[width=0.3\linewidth]{\img das_normal2.eps}\label{fig:das_shiftinvariant}}
\hfill{}
%\subfloat[]{\includegraphics[width=0.3\linewidth]{\img das_normal2.eps}\label{fig:das_shiftinvariant}}
\hfill{}
%\subfloat[]{\includegraphics[width=0.3\linewidth]{\img das_undersampled2_2x.eps}\label{fig:das_shiftvariant}}
}
\caption{LSV-plots of in-vivo data. a) Image of the data. b) Normal. c) Oversampling with phase rotation}
\label{fig:das}
\end{figure*}
